\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-27 paper.tex
Update on Overleaf.

We are currently setting up this kind of network in the framework of the European project MuMMER where a Pepper robot is intended to handle interactive situations in a Mall in Finland. One of the situation is a guiding task where Pepper will help people to find their route by pointing them landmarks and explaining them how to reach a destination. The use of \uwds enables to get knowledge about what the customer sees (or has seen) or not and to handle the task accordingly. We plan also to be able to add information coming from the dialogue (e.g. if the customer says that he has seen a particular landmark that could consequently be added to his belief world). Moreover, we plan also to use alternative world ability given by \uwds (as explained in \ref{alter}) (e.g. to create a world where we put )would be able to infer a possible world where the customer will be put in front of the desired shop to be able to explain him what he will see at destination.

>>>>

We are currently setting up this kind of network in the framework of the European project MuMMER where a Pepper robot is intended to handle interactive situations in a Mall in Finland. One of the situation is a guiding task where Pepper will help people to find their route by pointing them landmarks and explaining them how to reach a destination. The use of \uwds enables to get knowledge about what the customer sees (or has seen) or not and to handle the task accordingly. We plan also to be able to add information coming from the dialogue (e.g. if the customer says that he has seen a particular landmark that could consequently be added to his belief world). Moreover, we plan also to use alternative world ability given by \uwds (as explained in \ref{alter}) (e.g. to create a world where we put the customer in front of )would be able to infer a possible world where the customer will be put in front of the desired shop to be able to explain him what he will see at destination.
